
Guidance and glossary
===================================== 

#### Guidance: 

It is a requirement of membership to C40 for cities to have a Climate Action Plan (CAP) approved by C40 as in line with its CAP framework. Part of this framework and review process is to ensure that cities have ambitious citywide emission reduction targets informed by the goals of the Paris Agreement using C40’s Deadline 2020 research.

Cities are also required to report these targets as part of their annual reporting to CDP. However, many cities do not report their target data correctly to CDP, often it is incomplete or inaccurate, therefore the dataset behind this table serves as C40’s source of truth on city targets. 

The data is ‘cleaned’ annually to ensure that it is up to date. Nevertheless, the targets in this dataset are owned by the city and may be subject to change (e.g. if a new mayor decides to change the overarching target). Therefore, if you would like to prominently use a city from this table as an example, it is recommended to check for certainty that the target is still active in the city. 

The CAP team has been maintaining this dataset iteratively for many years, to keep an accurate and up-to-date track of city targets. 

The table in this tool shows only current (i.e. active) and complete targets. The back-end data also contains ‘historic’ (i.e. previous ‘2020’ targets) and ‘invalid’ (such as superseded or updated) targets, which are not displayed in this table. Targets in the table are only for the entire boundary of a city (‘city-wide’), and should align with the city’s GHG inventory boundary. 

This data has provided important functions within C40, such as research and analysis, KPI reporting and speech announcements, such as those that comment on the progress that cities are making towards their targets and the goals of the Paris Agreement. 
The data behind this table exists in C40’s python-based data warehouse, which is managed by the Analytics team. 

Moving forward, there is an intention from the CAP and Analytics teams to co-develop a more interactive dashboard that could also include additional insights, such as city emissions trajectories over time, key sectoral strategic objectives, and/or other indicators such as fossil fuel use or electricity emissions. However, this project is on hold until adequate resources are available. This table is intended as an interim resource.  

<br>

#### Glosary: 

```{r}
df_dicc <- readxl::read_xlsx(here("data/variables_glosary.xlsx"))
```

```{r}
df_dicc |> 
  janitor::clean_names() |> 
  gt() |> 
  tab_header(title = md("**Table glosary**")) |> 
  cols_label(
    variable = md("**Variable**"),
    description = md("**Description**")
  ) |> 
  sub_missing(
    columns = everything(),
    rows = everything(),
    missing_text = "-"
) |> 
  tab_style(
    style = cell_text(style = "italic"),
    locations = cells_body(
      columns = description
    )
  )
```